

\cvsection{PUBLICATIONS}
\href{https://doi.org/10.1145/3622839}{\textbf{Reusing Just-in-Time Compiled Code}}\newline
OOPSLA 2023, Cascais, Portugal.

{\it {\bf Meetesh Kalpesh Mehta}, Sebastián Krynski, Hugo Musso Gualandi, Manas Thakur, and Jan Vitek.}

\divider

\href{https://doi.org/10.1145/3623507.3623549}{\textbf{Debugging Dynamic Language Features in a Multi-tier Virtual Machine}}\newline

VMIL 2023, Cascais, Portugal.

{\it Anmolpreet Singh, Aayush Sharma, {\bf Meetesh Kalpesh Mehta}, and Manas Thakur.}

\cvsection{Professional \\\medskip Service}

\href{https://2024.splashcon.org/profile/meeteshkalpeshmehta}{\textbf{Part of OOPSLA 24 AEC}}\newline

Was part of the OOPSLA 2024 Artifact Evaluation Committee.
As a part of this service I evaluated six artifacts.

\cvsection{TALKS}

\textbf{Presented @ IICT 2024}\newline
Presented a talk titled ``Why generating TAC for JavaScript is hard?'' at IICT, Dayananda Sagar College of Engineering, Bangalore, India, Sep 28th—29th, 2024
\href{https://meetesh06.github.io/IICT-PPT-RC2.pdf}{Slides}, \href{https://www.youtube.com/watch?v=5yYm6mYRiO8}{Recording}

\divider

\textbf{Presented @ RHPL 2023}\newline
Presented a talk titled ``Reusing Just-in-Time Compiled Code'' at RHPL (co-located with FSTTCS 2023) IIIT Hyderabad, India, Dec 18th—20th, 2023
\href{https://meetesh06.github.io/RHPL-23.pdf}{Slides}, \href{https://fmindia.cmi.ac.in/rhpl/index.html}{Website}

\divider

\textbf{Presented @ VMIL 2023 remotely}\newline
Presented a talk titled ``Debugging Dynamic Language Features in a Multi-tier Virtual Machine'' at OOPSLA, Cascais, Portugal, October 23rd, 2023.
\href{https://meetesh06.github.io/VMIL-23-talk.pdf}{Slides}, \href{https://www.youtube.com/watch?v=pd_Px8LaHvw&t=20041s}{Recording}

\divider

\textbf{Presented @ SERI 2023}\newline
Presented a talk titled ``Debugging Contextually Specialized JIT Runtimes: Challenges and Strategies'' at Software Engineering Research in India (SERI) Goa University, India, June 2nd-3rd, 2023.
\href{https://meetesh06.github.io/seri-23-talk.pdf}{Slides}, \href{https://sites.google.com/view/seri-2023-goa/talks?authuser=0}{Website}
