\cvproject{Runtime vizualizer for contextual dispatch}
\begin{itemize}
\item Developed a runtime visualizer to study the impact of contextual dispatch on the \rsh{} Virtual Machine.
\end{itemize}

\cvproject{Points to debugger}
\begin{itemize}
\item For my mini project in the CS 611 (Program Analysis) course, I created a debugger for the vasco framework. This tool allows developers to visualize the points-to graph generation process in Java programs, providing valuable insights into program behavior.
\end{itemize}

\cvproject{XOPE Programming language}
\begin{itemize}
\item Developed as a part of B.Tech final year project, this is a compiler that implements a beginner friendly frontend and generates X86\_64 assembly. Made open source GitHub (\href{https://github.com/meetesh06/xope_4.2}{GitHub}).
\end{itemize}
\smallskip
\cvproject{Campus Story}
\begin{itemize}
\item Developed an app to simplify information flow in educational institutions to students. The app was developed using React Native for iOS, Android and web platforms. Made open source GitHub (\href{https://github.com/meetesh06/CampusStory}{GitHub}).
\end{itemize}
\smallskip
\cvproject{Compl-Validator}
\begin{itemize}
\item Developed as an aid to speedup assignment evaluation at IIT Mandi. This is a set of tools and libraries for backend/frontend to allow easier integration and evaluation of moodle submissions (\href{https://github.com/CompL-Research/CompL-Evaluator-Backend}{GitHub}).
\end{itemize}
\smallskip

\cvsection{Hobbies}

I like to spend my free time reading books, travelling and watching anime.
Some of my favourite books are: Crime and Punishment, The Trial, Metamorphosis, The Godfather, Project Hail Mary, Dune (the god emperor of dune is my favourite in the series), Pride and Prejudice, Palace of Illusions.
